% Author: Cristian Gonzales
% Created for Physical Time, 2018

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[document]{ragged2e}

\newcommand\tab[1][1cm]{\hspace*{#1}}

\begin{document}
	\Large{\textbf{Sprint 1 Report}}\\
	\Large{\textbf{Product: Physical Time iOS Application}}\\
	\Large{\textbf{Team: The Physical Time Team}}\\
	\Large{\textbf{Date: February 4, 2018}}\\
	
	\vspace{-3mm}
	
	\section{Actions to stop doing}
		\vspace{-3mm}
		\tab \normalsize{Based off our last sprint, we believe that we should stay committed to keeping sprint meetings on Wednesday and Friday over Skype or Google Hangouts. Either forum will suffice. We are not in close proximity of each other, so at the current time, this is most convenient.}
		
	\section{Actions to start doing}
		\vspace{-3mm}
		\tab \normalsize{Actions that we should partake in is better communication on forums such as Slack and being more organized with Scrum documents. We believe that fixing this will keep our developers focused, punctual, and in the loop of the current status of our sprint (outside of sprint meetings, that is). Also, we should keep disciplined on the key things that are needed to be discussed during the sprint meeting. Hence, we will follow the Scrum framework more religiously, and perform full stand-up meetings.}
		
	\section{Actions to keep doing}
		\vspace{-3mm}
		\tab \normalsize{Things we should continue to do that will keep the dynamic of our group healthy is contributing and having a voice at Scrum meetings. We believe that adding more functionality in early stages will set us up for success in the long run.}
		
	\section{Work completed \& not completed}
		\vspace{-3mm}
		\normalsize{The following user stories from the sprint plan were completed:}\\
		\vspace{-3mm}
		\begin{itemize}
			\item As a developer, I want to learn and get used to the frameworks, microframeworks, and development environment needed in order to build an iOS application.
		\end{itemize}
		\vspace{-3mm}
		\normalsize{The uncompleted user stories are as follows:}\\
		\vspace{-3mm}
		\begin{itemize}		
			\item As a developer, I want to be able to gather critical data points (e.g. sunrise and sunset) that will help visualize physical time relative to the user's location.
		\end{itemize}
		\vspace{-3mm}
		
	\section{Work completion rate}
		\vspace{-3mm}
		\normalsize{Sprint 1}\\
		\vspace{-3mm}
		\begin{itemize}
			\item Total number of user stories completed during the sprint: 1
			\vspace{-3mm}
			\item Total number of estimated ideal work hours completed during the sprint: 20
			\vspace{-3mm}
			\item Total number of days during the sprint: 14
		\end{itemize}
	
\end{document}
