% Author: Cristian Gonzales
% Created for Physical Time, 2018
%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[document]{ragged2e}
\usepackage{amssymb}

\newcommand\tab[1][1cm]{\hspace*{#1}}

\begin{document}
	\Large{\textbf{Sprint 3 Report}}\\
	\Large{\textbf{Product: Physical Time iOS Application}}\\
	\Large{\textbf{Team: The Physical Time Team}}\\
	\Large{\textbf{Date: March 4, 2018}}\\
	\Large{\textbf{Revised: March 7, 2018}}\\
	
	\vspace{-3mm}
	
	\section{Actions to stop doing}
		\vspace{-3mm}
		\tab \normalsize{We should stop being disorganized with branching and version control.}
		
	\section{Actions to start doing}
		\vspace{-3mm}
		\tab \normalsize{We should start enforcing coding guidelines/regulations and enforce peer reviews before commits and merges to the master branch.}
		
	\section{Actions to keep doing}
		\vspace{-3mm}
		\tab \normalsize{Things we should continue to do that will keep the dynamic of our group healthy is storytelling and Scrum meetings where all members are engaged and active. We are building momentum during the final stretch (sprint), so we need to keep it up.  We should continue having Wednesday workshops and storytelling sessions for the last sprint of this release.}
		
	\section{Work completed \& not completed}
		\vspace{-3mm}
		\normalsize{The following user stories from the sprint plan were completed:}\\
		\vspace{-3mm}
		\begin{itemize}
			\item As a user, I want to be able to enter my own values to manually augment the clock and see where the sun is based on the augmented clock (i.e. see what times sunrise, sunset, dusk, dawn occur according to the augmented clock).
			\item As a developer, I want to be able to dynamically change the back- ground based on the current time (so that it reflects the time of day, like night, nadir, et cetera).
		\end{itemize}
		\vspace{-3mm}
		\normalsize{The uncompleted user stories are as follows:}\\
		\vspace{-3mm}
		\begin{itemize}		
			\item As a developer, I want to start on the visualization to show the user where the sun is relative to where they are on the Earth.
		\end{itemize}
		\vspace{-3mm}
		
	\section{Work completion rate}
		\vspace{-3mm}
		\normalsize{Sprint 3}\\
		\vspace{-3mm}
		\begin{itemize}
			\item Total number of user stories completed during the sprint: 2
			\vspace{-3mm}
			\item Total number of estimated ideal work hours completed during the sprint: $\sim$ 30
			\vspace{-3mm}
			\item Total number of days during the sprint: 14
		\end{itemize}
	
\end{document}
