% Author: Cristian Gonzales
% Created for Physical Time, 2018

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[document]{ragged2e}
\usepackage{amssymb}

\newcommand\tab[1][1cm]{\hspace*{#1}}

\begin{document}
	\Large{\textbf{Sprint 2 Report}}\\
	\Large{\textbf{Product: Physical Time iOS Application}}\\
	\Large{\textbf{Team: The Physical Time Team}}\\
	\Large{\textbf{Date: February 18, 2018}}\\
	
	\vspace{-3mm}
	
	\section{Actions to stop doing}
		\vspace{-3mm}
		\tab \normalsize{We should stop being tardy to meetings, and we should also stop being lazy with our Scrum board.}
		
	\section{Actions to start doing}
		\vspace{-3mm}
		\tab \normalsize{We should start doing a peer programming workshop on Wednesdays, and we should also establish a sense of urgency in terms of meeting certain benchmarks during our sprint. Overall, our morale should be a little higher as a team. We should create more traffic through our communication channels and utilize our Scrum board more than it has been used.}
		
	\section{Actions to keep doing}
		\vspace{-3mm}
		\tab \normalsize{We should continue to keep our sponsor, Todd Anderson, in the loop about our progress, as we have continually been doing. We should also continue informal storytelling sessions that occur once a week (we don't have a set time for these informal meetings).}
		
	\section{Work completed \& not completed}
		\vspace{-3mm}
		\normalsize{The following user stories from the sprint plan were completed:}\\
		\vspace{-3mm}
		\begin{itemize}
			\item As a user, I want to see a augmented clock that displays a 24-hour time format in one clock rotation (usually 12 hours), with 4 hour divisions.
			\item As a user, I want to see a decent UI in the works so that I may eas- ily navigate the appli- cation and know the exact purpose it serves (with no prior knowledge of the application).
			\item As a developer, I want to integrate an easy-to-use visualization frame- work to create the clock (e.g. d3.js).
		\end{itemize}
		\vspace{-3mm}
		\normalsize{The uncompleted user stories are as follows:}\\
		\vspace{-3mm}
		\begin{itemize}		
			\item [None]
		\end{itemize}
		\vspace{-3mm}
		
	\section{Work completion rate}
		\vspace{-3mm}
		\normalsize{Sprint 2}\\
		\vspace{-3mm}
		\begin{itemize}
			\item Total number of user stories completed during the sprint: 3
			\vspace{-3mm}
			\item Total number of estimated ideal work hours completed during the sprint: $\sim$ 30
			\vspace{-3mm}
			\item Total number of days during the sprint: 14
		\end{itemize}
	
\end{document}
